\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-02-17 manuscript.Rnw
Minor fixes to use \pkg when was incorrectly using \code

As mentioned in the introduction, \code{heemod} is the only other general purpose \proglang{R} package for cost-effectiveness modeling. It differs from \pkg{hesim} in that it focuses solely on cDTSTMs (i.e., Markov cohort models) and is not designed to facilitate integration of economic models with the statistical models used for parameter estimation. Another important difference is that \code{hesim} is considerably faster since all simulations are vectorized (i.e, performed at the \proglang{C++} level). Performance comparisons are provided on the package website. The time-inhomogeneous total hip replacement example from \citet{briggs2006decision} was run with both packages using 1,000 PSA iterations. At the time of writing, a cohort model in \pkg{heemod} completed in approximately 1.9 minutes while the same cohort model took approximately 1 second to run in \pkg{hesim} and an equivalent individual-level simulation in \code{hesim} ran in 7.4 seconds.

>>>>

As mentioned in the introduction, \pkg{heemod} is the only other general purpose \proglang{R} package for cost-effectiveness modeling. It differs from \pkg{hesim} in that it focuses solely on cDTSTMs (i.e., Markov cohort models) and is not designed to facilitate integration of economic models with the statistical models used for parameter estimation. Another important difference is that \pkg{hesim} is considerably faster since all simulations are vectorized (i.e, performed at the \proglang{C++} level). Performance comparisons are provided on the package website. The time-inhomogeneous total hip replacement example from \citet{briggs2006decision} was run with both packages using 1,000 PSA iterations. At the time of writing, a cohort model in \pkg{heemod} completed in approximately 1.9 minutes while the same cohort model took approximately 1 second to run in \pkg{hesim} and an equivalent individual-level simulation in \pkg{hesim} ran in 7.4 seconds.
